IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
node

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
In Section~\ref{sec:retrofit}, however, we used only a simplified
language as an example target language.
%
In this section, we consider the application of our embedding to
JavaScript, and two other real world target languages, Haskell, and C.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

JavaScript, as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O
(we denote this language as |targetLangJS|).
%
When JavaScript is embedded in web browser engines such as
Gecko or Blink, or in server-side platforms such as Node.js, additional
APIs such as the Document Object Model (DOM) or the file system
get exposed as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  We, indeed, do this for the Gecko implementation when considering
  Web Workers that run operate OS threads.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

However, this issue of performance and JavaScript isolation is not
unique to our work. 
%
In particular, browser layout engines rely on the isolation of content
from different origins (e.g., two iframes of different origins) to
implement the \emph{same-origin policy}.
%
Since creating an OS thread for each iframe is expensive, both V8 and
SpiderMonkey provide a means for running JavaScript code in isolation,
on disjoint sub-heaps of the same OS thread.
%
In V8, this unit of isolation is called a \emph{context}~\tocite{}, in
SpiderMonkey, it called a \emph{compartment}~\tocite{}.
%
Each context/compartment is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
(Gecko and Node.js expose features such as the DOM and
filesystem by extending this global object.)
%

\subsubsection{Server-side embedding for Node.js}

Using contexts as the unit of isolation, we implemented
|specLangJS seqf| for Node.js.
%
Our implementation provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library and our IFC primitives (|send|, |sandbox|, etc.).
%
In turn, these tasks can create new tasks with |sandbox|.
%
Formally, |sandbox| is defined with |klone(tS) = tS0|, where |tS0| is
the global object corresponding to the standard JavaScript library and
our IFC primitives.

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced(left).}
\end{figure}
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
While V8 provides a means for sharing objects between contexts that
share a security token (in the case of Blink this is used by pages of
the same origin), our API (conservatively) restricts the kinds of
messages that can be exchanged.
%
More concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
However, our implementation is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

\Red{HERE}

>>>>

In the introduction, we stated that the original motivation behind
developing this embedding was in order to formally specify a
coarse-grained information flow control language for JavaScript.
%
Indeed, this work serves as the theoretical foundation for the
JavaScript IFC systems built atop Node.js and Gecko layout engine.
%
In this section, we consider the application of our embedding to
JavaScript for these two platforms, and two other real world target
languages, Haskell, and C.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different features and properties, as well as discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

JavaScript, as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O
(we denote this language as |targetLangJS|).
%
When JavaScript is embedded in web browser engines, such as Google's
Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
additional APIs such as the Document Object Model (DOM) or the file
system get exposed as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  Indeed, the Gecko implementation of this work does this for Web
  Workers that run operate OS threads~\cite{cowl}.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

However, this issue of performance and JavaScript isolation is not
unique to our work. 
%
In particular, layout engines rely on the isolation of content from
different origins (e.g., two iframes of different origins) to
implement the \emph{same-origin policy}.
%
Since creating an OS thread for each iframe is expensive, both
Google's V8 and Mozilla's SpiderMonkey provide a means for running
JavaScript code in isolation, on disjoint sub-heaps of the same OS
thread.
%
In V8, this unit of isolation is called a \emph{context}~\tocite{}; in
SpiderMonkey, it called a \emph{compartment}~\tocite{}.
%
Each context/compartment is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
(Gecko and Node.js expose features such as the DOM and
file system by extending this global object.)
%
Naturally, our notion of a task for JavaScript directly corresponds to
a context/compartment.
%
Below we describe some of the implementation details specific to
Node.js and Gecko.

\subsubsection{Server-side embedding: Node.js}

We implemented |specLangJS seqf| for Node.js in the form of a module
(library), which does not modify the Node.js or V8 code-base in any
way.
%
Our implementation provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library and our IFC primitives (|send|, |sandbox|, etc.).
%
In turn, these tasks can create new tasks with |sandbox|.
%
In our formal treatement, |sandbox| is defined with |klone(tS) = tS0|,
where |tS0| is the global object corresponding to the standard
JavaScript library and our IFC primitives.

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced(left).}
\end{figure}
%
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
(This task is part of the trusted computing base (TCB) and has access
to the full Node.js API.)
%
While V8 provides a means for sharing objects between contexts (used
by same-origin contexts in Blink), our system conservatively restricts
the kinds of messages that can be exchanged by tasks.
%
Concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
Our implementation, however, is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

\subsubsection{Client-side embedding: Gecko}
\Red{HERE}
